### 2015-02-03 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: minor update to report

On February 24, 2012, a fire in residential structure injured seven Prince George's County firefighters. NIST examined the fire dynamics of this incident at the request of the Prince George's Country Fire/Emergency Medical Services (EMS) Department. Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this single-story residential structure using physics-based calculations.
\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
\end{enumerate}

>>>>

On February 24, 2012, a fire in residential structure injured seven Prince George's County firefighters. NIST examined the fire dynamics of this incident at the request of the Prince George's Country Fire/Emergency Medical Services (EMS) Department. Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire. The specific objectives of the simulations detailed in this report are: 
\begin{enumerate}
\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this single-story plus basement residential structure using physics-based calculations.
\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
\item To provide a basis for discussing tactical operations.
\end{enumerate}
